%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {R\&D Software Engineering Intern} % Job title
    {Brain Corporation} % Organization
    {San Diego, CA} % Location
    {Jun. 2018 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Collaborated on a code base of 1 Million+ lines of code using
          GitHub.}
        \item {Researched and implemented new motion planning algorithms for a
          ground robot.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Graduate Researcher} % Job title
    {MAGICC Lab, Brigham Young University} % Organization
    {Provo, UT} % Location
    {Sep. 2016 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researching autonomous landing of multirotor UAVs on moving
          platforms.}
        \item {Experience wrigin custom control and navigation code for
          fixed-wing and multirotor UAVs.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Mechanical Engineering Intern} % Job title
    {ADSYS Controls Inc.} % Organization
    {Irvine, CA} % Location
    {May 2016 - Aug. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created methods and fixtures for testing precision of 4-axis gimbal
          to 100's of $\mu$Rad.}
        \item {Presented work weekly to CEO and head engineers.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Mechanical Engineering Intern} % Job title
    {Aerofit LLC.} % Organization
    {Fullerton, CA} % Location
    {May 2015 - Aug. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Trained department leader and employees for new \$10 million/yr.
          product line.}
        \item {Planned and oversaw testing of over 400 hydraulic fittings for
          aerospace applications.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
